Think deep for reef resilience

### 2025-08-09 paper/paper_draft.qmd
95th percentile description

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 2.5 to 97.5 percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
width="14.82cm"}

@@

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
represented five times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
width="14.82cm"}

![Reef area-relative coral cover timeseries clustered within each management area, for each
GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 2.5 to 97.5 percentile confidence intervals. Each management area is
represented five times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
width="14.82cm"}

>>>>

![Degree Heating Week timeseries (in °C - Weeks) for the GCMs selected. Colours represent
the different management areas across the Great Barrier Reef. Green represents
Cairns-Cooktown, orange represents Far-Northern, blue represents Mackay-Capricorn and red
represents the Townsville-Whitsunday management area. Solid lines represent the
management-area median timeseries and bands represent the 95th percentile confidence
intervals.](../outputs/ADRIA_results/HighResCoralStress/figs/methods_dhw_timeseries.png){#fig-methods-dhws
width="14.82cm"}

@@

![Reef Degree Heating Week timeseries clustered within each management area, for each GCM
analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 95th percentile confidence intervals. Each management area is represented five
times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_dhw_timeseries_plot.png){#fig-gcm-dhw-trajectories
width="14.82cm"}

![Reef area-relative coral cover timeseries clustered within each management area, for each
GCM analysed. ‘Low’ clusters (green) are clusters with the lowest median area-relative cover
between 2030 and 2040 within each bioregion. ‘Medium’ clusters (orange) are clusters with
intermediate median area-relative cover between 2030 and 2040 within each bioregion. ‘High’
clusters (blue) are clusters with the highest median area-relative cover between 2030 and
2040 within each bioregion. Solid lines represent the cluster median timeseries and bands
represent the 95th percentile confidence intervals. Each management area is represented five
times (for each GCM), with each GCM displayed
horizontally.](../outputs/ADRIA_results/HighResCoralStress/figs/GCM_cover_timeseries_plot.png){#fig-gcm-cover-trajectories
width="14.82cm"}
